Supplemental Information: Gas exchange in large rivers controlled by hydraulic geometry: implications for remotely sensing gas exchange via the SWOT satellite

### 2021-09-14 supp_v5.Rmd
big ms_v5 push

---
title: "Supplemental Information: Gas exchange in large rivers controlled by hydraulic geometry: implications for remotely sensing gas exchange via the SWOT satellite"
author: "CB Brinkerhoff, CJ Gleason, CJ Zappa, PA Raymond, MH Harlan"
date: "`r Sys.Date()`"
csl: agu_citation_style.csl
output:
  word_document: 
      reference_docx: word-styles-reference.docx
bibliography: References.bib

@@

##Contents
This supplementary information contains 4 texts, 4 figures and 2 tables. Please consult https://github.com/craigbrinkerhoff/RSK600 for all code to build and generate results, figures, and the manuscript.

@@

##Figures
![Figure S1: Flowchart of the entire study's workflow](cache/flowchart.jpg)

![Figure S2 Timeseries of the biweekly CO2 data from @beaulieuControlsGasTransfer2012a. Sampling took place 2008-2009 in the Ohio River (upstream of Cincinnati, Ohio, United States). Each point here was joined to the 11-day SWOT observations used in this study (section 2.4).](cache/FCO2/Beaulieu_timeseries.jpg)

![Figure S3 All timeseries of k per river](cache/validation/timeseries_noerr.jpg)

##Tables
*Table S1: Validation metrics used in this study, where r is the correlation coefficient, Nt is number of observations and i is the specific observation. σ refers to the variance of the sample and μ refers to the mean of the sample. As is standard, a carrot accent indicates the predicted value.*

@@

*Table S2: Details on the 3 depth hydraulic geometry models used to estimate FCO2 from the SWOT rivers (section 2.4).*

@@

##References

>>>>

---
title: "Supplemental Information: Gas exchange in large rivers controlled by hydraulic geometry: implications for remotely sensing gas exchange via the SWOT satellite"
author:
  - Craig B Brinkerhoff:
      email: cbrinkerhoff@umass.edu
      institute: UMass
      correspondence: true
  - Colin J Gleason:
      institute: UMass
  - Christopher J Zappa:
      institute: Lamont
  - Peter A Raymond:
      institute: Yale
  - Merritt H Harlan:
      institute: UMass
institute:
  - UMass: Department of Civil & Environmental Engineering, University of Massachusetts, Amherst, MA
  - Lamont: Lamont-Doherty Earth Observatory, Columbia University, Palisades, NY
  - Yale: School of the Environment, Yale University, New Haven, CT
bibliography: References.bib
csl: agu_citation_style.csl
output:
  word_document:
      pandoc_args:
        - '--lua-filter=scholarly-metadata.lua'
        - '--lua-filter=author-info-blocks.lua'
      reference_docx: word-styles-reference.docx

@@

## Contents
This supplementary information contains 4 texts, 3 figures and 2 tables. Please consult https://github.com/craigbrinkerhoff/RSK600 for all code to build and generate results, figures, and the manuscript.

@@

## Figure S1
![Figure S1: Flowchart of the entire study's workflow](cache/flowchart.jpg)

## Figure S2
![Figure S2 Timeseries of the biweekly CO2 data from @beaulieuControlsGasTransfer2012a. Sampling took place 2008-2009 in the Ohio River (upstream of Cincinnati, Ohio, United States). Each point here was joined to the 11-day SWOT observations used in this study (section 2.4).](cache/FCO2/Beaulieu_timeseries.jpg)

## Figure S3
![Figure S3 All timeseries of k per river](cache/validation/timeseries_noerr.jpg)

## Table S1
*Table S1: Validation metrics used in this study, where r is the correlation coefficient, Nt is number of observations and i is the specific observation. σ refers to the variance of the sample and μ refers to the mean of the sample. As is standard, a carrot accent indicates the predicted value.*

@@

## Table S2
*Table S2: Details on the 3 depth hydraulic geometry models used to estimate FCO2 from the SWOT rivers (section 2.4).*

@@

## References
